Meta-analytic approaches and effect sizes to account for 'nuisance heterogeneity' in comparative physiology

### 2021-09-17 MS/ms.Rmd
Fixed MS
Fixed Figure 1 and 3 legends

```{r, fig1, fig.cap="**Sources of effect size heterogeneity in meta-analyses**. Heterogeneity can come in various forms, from effect measures varying as a result of shared evolutionary history (i.e., phylogeny), the different trait types measured, and sources of 'nuisance heterogeneity'. In this example, nuisance heterogeneity is generated by differences in the experimental temperatures at which the animals were tested. However, nuisance heterogeneity can come in various other forms such as differences in dosage. We can control for these types of heterogeniety by reformalising effect sizes and/or using multilevel metaregression."}
image <- image_read(here::here("figs", "Fig1_v2_ML.png"))
image
```

@@

## **Opening Up New Opportunities in Comparative Physiology: Expanding the Breadth of Effect Sizes to Deal with "Nuisance Heterogeneity"**

@@

```{r, fig0, fig.cap="**Effect sizes from old to new**. ‘Traditional’ effect sizes (top left) are somehow detached from more biologically relevant measures commonly used in ‘Comparative physiology’ (top right) although statistical connections have always existed (‘Universal’; top middle). By combining traditional effects with physiological parameters, and correcting the resulting quantities for nuisance variation, we can derive a new generation of biologically relevant, easily interpretable effect measures for use in meta-analyses (‘Expanded’; bottom). For abbreviations, see Table 1."}
image <- image_read(here::here("figs", "Fig0_v1_ML.png"))
image
```

>>>>

```{r, fig1, fig.cap="**Sources of effect size heterogeneity in meta-analyses**. Heterogeneity can come in various forms, from effect measures varying as a result of shared evolutionary history (i.e., phylogeny), the different trait types measured, and sources of 'nuisance heterogeneity'. In this example, nuisance heterogeneity is generated by differences in the experimental temperatures at which the animals were tested ('gray' shaded area on top). However, nuisance heterogeneity can come in various other forms such as differences in dosage. We can control for these types of heterogeniety by reformalising effect sizes and/or using multilevel metaregression ('white' area on the bottom)."}
image <- image_read(here::here("figs", "Fig1_v2_ML.png"))
image
```

@@

## **Opening New Opportunities in Comparative Physiology: Expanding the Breadth of Effect Sizes to Deal with "Nuisance Heterogeneity"**

@@

```{r, fig0, fig.cap="**Effect sizes from old to new**. ‘Traditional’ effect sizes (top left) are somehow detached from more biologically relevant measures commonly used in ‘Comparative physiology’ (top right) although statistical connections have always existed (‘Universal’; top middle). By combining traditional effects with physiological parameters, and correcting the resulting quantities for nuisance variation, we can derive a new generation of biologically relevant, easily interpretable effect measures for use in meta-analyses (‘Expanded’; bottom). For abbreviations of common effect sizes see Table 1. lnRRQ10 = Q10 response ratio; lnCVRQ10 = log Q10 coefficient of variation ratio; SMDT = Temperature corrected standardised mean difference; ARR = acclimation response ratio."}
image <- image_read(here::here("figs", "Fig0_v1_ML.png"))
image
```
